---
title: "gapminder data"
author: "Evelyn Takyi, Vida Osei"
date: "March 1, 2017"
output:
  html_document: default
  pdf_document: default
---
```{r echo=FALSE, include=FALSE}
library(ggplot2)
library(plyr)
library(curl)
```




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(curl)
gapminder_locations<-curl(url="https://raw.githubusercontent.com/resbaz/r-novice-gapminder-files/master/data/gapminder-FiveYearData.csv")
gapminder<-read.csv(gapminder_locations)
head(gapminder)
```

```{r }

```




# Structure  of the gapminder data
```{r echo=FALSE}
str(gapminder)

```
```{r}
summary(gapminder)

```
# Total GDP by Continent 
### The plot below shows the total GDP of continent in the world. Among the various continents, oceania showed the least Gdp and America showed the highest Gdp with respect to the years. The  p-value of less than 0.005 and the R-squared value of 0.05112 showed a strong relationship between the continents and the GDP values over the years. 
```{r echo=FALSE}
GDP_Trend <- ddply(gapminder, ~country + year + continent, summarize, GDP = gdpPercap * pop, pop = pop)
GDP_Continent <- ddply(GDP_Trend, ~year + continent, summarize, TotalGDP = sum(GDP), Totalpop = sum(pop))
ggplot(GDP_Continent, aes(x =year, y = TotalGDP, colour = continent)) + geom_line()+
ggtitle("Total GDP by Continenet")
annotate("text", x = 1960, y = 1.5e+13, label = " r= 0.2 \nP = 2.2e-16")

```


# The Mean LifeExpectancy by Countries
### The plot below shows the mean life expectancy of people by countries from different continent. Canada and Mexico hve high Life expectancies. That of Kenya has been increasing over the years but has been decreasing in the 1990's. Life expectancy of Cambodia was very low but has been increasing in recent years.
```{r echo=FALSE}
Countries_bar <- c("Canada", "Kenya", "Cambodia", "Mexico")
ggplot(subset(gapminder, country %in% Countries_bar), aes(x = year, y = lifeExp, color = country))+ 
  geom_line()+ 
  geom_point()+
  ggtitle("Life Expectancy of Countries")
```


# Population and the year
### The plot below shows the mean population from 1952 to 2007 of people in various continent of the world. The mean population of Asia is high and has been increasing over the years. Population of the other continents is low and with gradual increment in recent years compared to Asia. The P-value and R -squared values shows significant relationship  between population and the years of each continent and the years. 
```{r echo=FALSE}
GDP_Trend <- ddply(gapminder, ~country + year + continent, summarize, pop = pop)
GDP_Continent <- ddply(GDP_Trend, ~year + continent, summarize, pop = mean(pop))
ggplot(GDP_Continent, aes(x =year, y = pop, colour = continent)) + 
  geom_line()+
  ggtitle("Population of Continents")+annotate("text", x = 1960, y = 1.0e+08, label = " r= 0.08 \nP < 0.005")
```


#Graph of Life Expectancy and Population by Continent
### The graph below shows population of the continents and their life expectancies. r and p values shows there is no relationship or correlation between these variables.
```{r echo=FALSE}
ggplot(gapminder, aes(x = pop, y = lifeExp, colour = continent,)) +
  geom_point() +scale_x_log10()  +geom_smooth(method = 'lm')+
  ggtitle("Life Expectancy vrs Population by Continent")+annotate("text", x = 1e+05, y = 80, label = " r= 0.06 \nP > 0.007")
```

