---
title: "gapminder data"
author: "Evelyn Takyi"
date: "March 1, 2017"
output:
  html_document: default
  pdf_document: default
---

# Load gapminder data changes
```{r echo=FALSE}
library(curl)
gapminder_locations<-curl(url="https://raw.githubusercontent.com/resbaz/r-novice-gapminder-files/master/data/gapminder-FiveYearData.csv")
gapminder<-read.csv(gapminder_locations)
head(gapminder)
```

```{r echo=FALSE}
library(ggplot2)
library(dplyr)
library(curl)
```




# Structure  of the gapminder data
```{r echo=FALSE}
str(gapminder)

```
```{r}
summary(gapminder)

# Plots
```{r Plot of lifeExp by gdpPercap to indicate any linear relationship between them}
ggplot(gapminder, aes(x = gdpPercap, y = lifeExp, colour = continent)) +
  geom_point()  + geom_smooth(method = 'lm') +
 scale_x_log10() + geom_smooth(method = 'lm') 
```


```{r}
ggplot(gapminder, aes(x = year, y = lifeExp, group = country, width = 3.5, height = 2.5)) +
  geom_line(aes(colour = continent))
```










```{r}
reg <- lm(lifeExp ~ gdpPercap, data=gapminder)
summary(reg)

```
# new
```{r}
ggplot(gapminder, aes(x = year, y = lifeExp, group = country, width = 3.5, height = 2.5)) +
  geom_line(aes(colour = continent))  + facet_wrap(~ continent) +theme_classic()
```


```{r}
gre <- lm(lifeExp ~ year, data=gapminder)
summary(gre)
```




